%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GG Professional CV
% LaTeX Template
% Version 0.1 (5/9/22)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\name{Luigi}{Clemente}
\position{Software Engineer}
\github{gigitsu}
\mobile{(+39) 328-5409008}
\linkedin{luigi-clemente-g2}
\email{luigi.clemente@gsquare.it}

%-----------------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-----------------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Bending Spoons S.p.A.}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Backend Engineer}
% How the letter is closed
\letterclosing{Sincerely,}

%-----------------------------------------------------------------------------------------
\begin{document}
% Print the title with above letter information

\makelettertitle

%-----------------------------------------------------------------------------------------
%	LETTER CONTENT
%-----------------------------------------------------------------------------------------

\begin{cvletter}

\lettersection{About Me}
I'm Luigi, a software engineer with 12 years of experience in many different areas of software. Most of my experience lies in full stack development with more focus on backend development. During my
career, I have crafted C\# Windows applications with some highly optimized code written directly in IL, web applications tailored to customer needs using technologies like Angular, TypeScript, SASS and
many PHP backend frameworks and in the last 5/6, I focused mainly in functional programming using technologies such as Scala, Akka and Elixir. \\ I often start personal projects just for the fun of
learning new skills.  I have recently made a personal zsh framework (like oh-my-zsh but much more simple and lightweight), started studying Rust to make a PR on an open source project and started writing
an SQLite clone in C just to learn better databases internals.

\lettersection{Why Bending Spoons?}
I'm impressed by the quality of your products and the number of people it reaches. I like the idea to build something that can have an impact on people's day-by-day life. I'm also very curious about the technologies
you have developed! I did some experiments in video editing in the past (very amatorial), I have always been fascinated by these pieces of technologies and I'm thrilled to know how Fellini works. Furthermore, when I 
was in Milan, I participated in some of your meetups and the environment you have built seemed compelling and challenging, full of skilled and passionate people. An environment in which I feel I can contribute
and grow.

\end{cvletter}

%-----------------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
%-----------------------------------------------------------------------------------------

\makeletterclosing

\end{document}