%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Luigi Clemente} % Your name
\address{github.com/Gigitsu \\ Skype: luigi.clemente.g2} % Your address
\address{+39 328-540-9008 \\ luigi.clemente@gsquare.it} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{AgileLab}{October 2020 - Preset}{Data Engineer}{Milan}
\item Design and development of DataMesh platform for the Enel data warehouse using Dremio, Spark, Springboot with Java, Scala and python
\end{rSubsection}

\begin{rSubsection}{Dottori.it}{September 2019 - October 2020}{Senior Software Engineer}{Milan}
\item Development and maintenance of Dottori.it, a web platform that aims to help people find the best doctor for their needs.
\item Desing and development of a microservices architecture using Elixir, Phoenix and Ecto with PostgreSQL.
\item Desing and development of services unit tests using ExUnit.
\item Services deployment on Kubernetes cluster.
\end{rSubsection}

\begin{rSubsection}{ATS S.p.A.}{October 2018 - August 2019}{Full Stack Developer | DevOps (as ApuliaSoft external consultant)}{Milan}
\item Development of BlinkS platform, a digital marketplace for non performing loans trading.
Restful backend written in Scala with AkkaHttp and Angular for the frontend.
\item Design and development of rest api and Angular components.
\item Design and development of unit test (using ScalaTest, ScalaMock and scala macro).
\item Design and development of release and build pipelines using GitLab CI tools.
\item Configuration of test and production environment on Azure (Kubernetes, MySQL).
\item Application deploy on Kubernetes.
\item Securing application using ModSecurity with CRS and custom rules on ingress nginx.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{SIA S.p.A.}{January 2018 - September 2018}{Backend Developer (as ApuliaSoft external consultant)}{Milan}
\item Development of the new version of the message broker of PagoPA\textregistered~system (named ``Nodo dei Pagamenti SPC"),
a reactive system which uses Scala, scalaxb, Akka and Akka Cluster to handle payments flows between the involved stakeholders and the government.
\item Design and development of tests for ``Nodo dei Pagamenti SPC" (using Scalatest).
\item Design and development of application-based release pipelines with Jenkins.
\item Release of application components on OpenShift cluster in test environment.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Exprivia S.p.A.}{May 2016 - December 2017}{Lead Developer (as ApuliaSoft external consultant)}{Molfetta}
\item Design and development of an engine, using TypeScript and Angular2,
able to emulate Oracle Forms functionality and therefore run old oracle forms application on modern browsers.
\item Maintenance of a tool to convert Oracle Forms save files into JSON/TypeScript format files, using Java and ANTLR.
\item Use of git and gitflow to manage the development process.
\item Design and development of widgets for the home banking of Banca Mediolanum, using Google Closure lib, D3js and C3js.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{ApuliaSoft S.r.l.}{October 2015 - August 2019}{Senior Developer}{Bari}
\item Development of www.dolcidee.it, a web community where people can share recipes and cooking advice, using PHP and Symfony 2.
\item Design and development of a Slack bot, written in JavaScript and deployed on Heroku, that help monitoring activities and
happiness of the employees through questions made by the bot at the end of every working days.
\item Design and development of a tool to optimize the disposition of articles into pallet displays for supermarkets, using TypeScript and Angular2.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{My Special Gift S.r.l.s., Startup}{April 2013 - May 2014}{Full Stack Developer}{Bari}
\item Design and development of the My Special Gift platform through which you can create shared gift lists and where your friends can pay a stake through a PayPal account, using HTML, CSS and PHP with Yii.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{DigitalCopy S.r.l.}{August 2010 - March 2013}{Developer}{Altamura (BA)}
\item Design and development of a cash register software and a management software for small and medium sized supermarket, using C\# .NET 4 with Microsoft WPF, nHibernate with SQLServer and dapper.net with sqlite
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Operating Systems & MacOS, Linux, Windows \\
Main programming languages & Elixir, Scala, Java, TypeScript, C\# \\
Other scripting languages and runtime & Node.js, PHP, Python, R, SQL \\
Frameworks and libraries & Phoenix, Ecto, Apache Spark, Akka \\
RDBMS & MySQL, PostgreSQL, SQL Server \\
NoSQL & MongoDB, Elasticsearch, Redis \\
Other software & Git, IntelliJ, Vim, VS Code, Kibana \\
Others & Docker, Jenkins, Microsoft Azure, Kubernetes \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{University of Bari ``Aldo Moro"}{April 2016}{BCs in Computer Science, 110/110}{Bari}
Thesis: Applicazioni di Reti Neurali Ricorrenti al PoS-Tagging di Testi
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}

\begin{rSubsection}{The Linux Foundation}{2021}{}{}
\item Certified Kubernetes Administrator (License number: LF-c55jbv7gct)
\end{rSubsection}

\begin{rSubsection}{Coursera}{2017}{}{}
\item Functional Programming Principles in Scala (License number: 85UUFRQVJ75F)
\item Functional Program Design in Scala (License number: BYV4DHVGYYDU)
\item Parallel programming (License number: 6BX9A2UTCGAX)
\end{rSubsection}

\begin{rSubsection}{MongoDB University}{2014}{}{}
\item M101P MongoDB for Developers
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Italian & Native speaker \\
English & Intermediate level, written and spoken
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
